Sonifying Quantum Superpositions by Correlating State Probability to Rhythmic Density

### 2023-09-15 isqcmc2023_latex/paper_isqcmc.tex
push latest paper revsion updates

\address{Jacobs School of Music -- Indiana University Bloomington\\
         107 S. Indiana Ave. - 47405 - Bloomington - Indiana - United States of America
         \email{walksmit@iu.edu, dvolkov@iu.edu, alealani@iu.edu}
}

@@

Our approach to sonifying a quantum state is as follows: first, calculate the probability of measurement for each of the basis states, then use these probabilities as input to one of several rhythmic density based sonification algorithms. These sonification algorithms map a higher probability to higher rhythmic density with faster rhythms and more notes, while lower probabilities correlate to lower rhythmic density with slower rhythms and less notes. As we outline later in the paper, rhythmic density is highly quantifiable for the human ear compared to other potential "sonification dimensions,". While our approach is infeasible to run on quantum hardware (because a useful approximation of the probabilities of a quantum state on hardware requires many invocations of the same program), it is still a useful sonification method for smaller simulated quantum systems. Further development of this method may have the potential to yield pedagogical, analytical, and creative tools for scientists and musicians.

>>>>

\address{Jacobs School of Music -- Indiana University Bloomington\\
         107 S. Indiana Ave. - 47405 - Bloomington - Indiana - United States of America
         \email{walksmit@alumni.iu.edu, dvolkov@iu.edu, alealani@iu.edu}
}

@@

Our approach to sonifying a quantum state is as follows: first, calculate the probability of measurement for each of the basis states, then use these probabilities as input to one of several rhythmic density based sonification algorithms. These sonification algorithms map a higher probability to higher rhythmic density with faster rhythms and more notes, while lower probabilities correlate to lower rhythmic density with slower rhythms and less notes. As we outline later in the paper, rhythmic density is highly quantifiable for the human ear compared to other potential sonification dimensions. While our approach is infeasible to run on quantum hardware (because a useful approximation of the probabilities of a quantum state on hardware requires many invocations of the same program), it is still a useful sonification method for smaller simulated quantum systems. Further development of this method may have the potential to yield pedagogical, analytical, and creative tools for scientists and musicians.
